Title

### 2024-01-29 Christine Chan/CF Registry/cf_registry_analysis.qmd
formatting

```{r}
# Formula for base model
x <- c(
  "age_group", "Gender", "bmi_perc", "MutClass", "A_IsOnEnzymes",
  "tube_feeding", "liver_disease",
  "A_FEV1_pct_predicted", "NumPulmExacerbation",
  "A_pulmonarycomplications1", "A_corticosteroids1"
)
y <- "Surv(tstart, tstop, cfrd_status_annual)"
f <- as.formula(paste0(y, "~", paste0(x, collapse = "+")))
cox_res <- coxph(f, data = s, cluster = eDWID)
# Plot survival
ggsurvplot(survfit(cox_res),
  data = s, risk.table = T, cumevents = T, fun = "event",
  xlim = c(2003, 2018), break.x.by = 1
)
# Forest plot and coefficients table
ggforest(cox_res, data = s)
# Diagnostics
test.ph= cox.zph(cox_res)
ggcoxzph(test.ph)
# ggcoxdiagnostics(cox_res,type = "martingale")
# ggcoxdiagnostics(cox_res,type = "deviance")
# ggcoxdiagnostics(cox_res,type = "score")
# ggcoxdiagnostics(cox_res,type = "schoenfeld")
```

@@

```{r}
s_split <- survSplit(Surv(tstart, tstop, cfrd_status_annual) ~ .,
  data = s, cut = 2003:2018, episode = "tgroup"
)
cox_res_split <- coxph(update(f, . ~ Gender:strata(tgroup)), data = s_split,
                       cluster = eDWID)
t = tidy(cox_res_split,exponentiate = T)
```

>>>>

```{r}
# Formula for base model
x <- c(
  "age_group", "Gender", "bmi_perc", "MutClass", "A_IsOnEnzymes",
  "tube_feeding", "liver_disease",
  "A_FEV1_pct_predicted", "NumPulmExacerbation",
  "A_pulmonarycomplications1", "A_corticosteroids1"
)
y <- "Surv(tstart, tstop, cfrd_status_annual)"
f <- as.formula(paste0(y, "~", paste0(x, collapse = "+")))
cox_res <- coxph(f, data = s, cluster = eDWID)
# Plot survival
ggsurvplot(survfit(cox_res),
  data = s, risk.table = T, cumevents = T, fun = "event",
  xlim = c(2003, 2018), break.x.by = 1
)
# Forest plot and coefficients table
ggforest(cox_res, data = s)
# Diagnostics
test.ph <- cox.zph(cox_res)
ggcoxzph(test.ph)
# ggcoxdiagnostics(cox_res,type = "martingale")
# ggcoxdiagnostics(cox_res,type = "deviance")
# ggcoxdiagnostics(cox_res,type = "score")
# ggcoxdiagnostics(cox_res,type = "schoenfeld")
```

@@

```{r}
s_split <- survSplit(Surv(tstart, tstop, cfrd_status_annual) ~ .,
  data = s, cut = 2003:2018, episode = "tgroup"
)
cox_res_split <- coxph(update(f, . ~ Gender:strata(tgroup)),
  data = s_split,
  cluster = eDWID
)
t <- tidy(cox_res_split, exponentiate = T)
```

### 2024-01-29 Quarto Template.qmd
formatting

```{r setup}
#| include: false
library(tidyverse)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

>>>>

```{r setup}
#| include: false
library(tidyverse)
switch(Sys.info()[["sysname"]],
  Windows = {
    home_dir <- "C:/Users/timvigers/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry"
  },
  Darwin = {
    home_dir <- "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry"
  }
)
knitr::opts_knit$set(root.dir = home_dir)
```
